Bow shocks, bow waves, and dust waves. II. Beyond the rip point

### 2019-03-14 papers/Papers1234/app-dust-wave.tex
Submit BS-BW-DW-01 paper
Write lots of discussion for Paper II

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/dust-trajectories}
  (b)\\
  \includegraphics[width=\linewidth]{figs/dust-divergent}
  \caption[Dust grain trajectories]{Dust grain trajectories under
    influence of a repulsive central \(r^{-2}\) radiative force.
    (a)~A parallel stream of dust grains approach from the right at a
    uniform velocity and with a variety of impact parameters (initial
    \(y\)-coordinate). The central source is marked by a red star at
    the origin, and its radiative force deflects the trajectories into
    a hyperbolic shape, each of which reaches a minimum radius marked
    by a small black square.  The incoming hyperbolic trajectories are
    traced in gray and the outgoing trajectories are traced in red.
    The locus of closest approach of the outgoing trajectories is
    parabolic in shape (traced by the thick, light gray line) and this
    constitutes the inner edge of the bow wave.  (b)~The same but for
    a divergent stream of dust grains that originates from a source on
    the \(x\) axis at a distance \(D = 10 R\starstar\) from the origin.  In
    this case, the inner edge of the bow wave is hyperbolic and the
    parallel stream result is also shown for comparison.}
  \label{fig:dust-trajectories}
\end{figure}

@@

If \(\frad\) is the only force experienced by the grain, then it will
move on a \textit{ballistic} trajectory, determined by its initial
speed at large distance, \(v_\infty\), and its impact parameter, \(b\).
For \(b = 0\), the grain radially approaches the source with initial
radial velocity \(-v_\infty\), which is decelerated to zero at the distance
of closest approach, \(R\starstar\), given by energy conservation:
\begin{equation}
  \label{eq:dust-r0}
  R\starstar = \frac{\kappa\grain L} {2 \pi c v_\infty^2} \ ,
\end{equation}
where we have defined a frequency-averaged single-grain opacity
(\si{cm^2.g^{-1}}) as
\begin{equation}
  \label{eq:kappa-grain}
  \kappa\grain = \frac{\pi a^2}{m\grain L} \int_0^\infty \Qp \, L_\nu \, d\nu \ ,
\end{equation}
in which \(m\grain\) is the grain mass and \(L\) is the bolometric
source luminosity.  The grain then turns round and recedes from the
source along the same radius, reaching a velocity of \(+v_\infty\) at large
distance.  Note that \(R\starstar\) as given by
equation~\eqref{eq:dust-r0} is formally identical to Paper~I's
equation~(6), but with the important difference that it is for a
single grain considered in isolation, rather than a well-coupled dusty
plasma.  If

@@

If the incoming dust grains initially travel along parallel
trajectories with varying \(b\), but the same \(v_\infty\), then deflection
by the radiative force will form a bow-shaped dust wave around the
radiation source, as shown in Figure~\ref{fig:dust-trajectories}.
However, the inner edge of the dust wave, \(R_{\text{in}}(\theta)\) is not
given by the closest approach along individual trajectories,
\(R\grain(\thm; b)\), but instead must found by minimizing
\(R\grain(\theta; b)\) over all \(b\) for each value of \(\theta\), which yields
\begin{equation}
  \label{eq:dust-r-in}
  \frac{R_{\text{in}}(\theta)} {R\starstar} = \frac{2}{1 + \cos\theta} \ .
\end{equation}
This is the polar form of the equation for the confocal parabola,
which we have already discussed in detail in \S~\ref{Q-sec:conic} and
Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  Its
planitude and alatude are \(\Gamma = \Lambda = 2\) and these are
unchanged under projection at any inclination.

@@

We will show later in \S~\ref{sec:magn-effects-grain} that for
sufficiently small grains the Larmor magnetic gyration radius, \(r\B\),
is typically small compared with other length scales of interest, and
so the grains are effectively tied to the magnetic field lines.  In
this approximation, we can calculate the grain dynamics in the
drag-free limit using \(f\rad\) as the sole force as above, but this
time allowing acceleration only along the field lines.  Assuming a
uniform magnetic field, the only extra parameter needed is
\(\theta\B\), the angle between the field direction and the direction of
the dust stream (assumed to be plane parallel).

@@

For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
the motion in the \(y\) direction obeys the ODE:
\begin{equation}
  \label{eq:ode-perp-bfield}
  \frac{d^2 y}{d x^2} = \tfrac12 R\starstar  \,
  y \, \bigl( x^2 + y^2\bigr)^{-3/2} \ .
\end{equation}
We have been unable to find an analytic solution to this equation, but
a numerical solution is shown in Figure~\ref{fig:inertia-thB90}.  When
the impact parameter is larger than \(b \sim R\starstar\), the
trajectories are very similar to in the non-magnetic case
(Fig.~\ref{fig:dust-trajectories}a).  As shown in
Figure~\ref{fig:inertia-thB90}b, the interaction of the grain with the
radiation field in this large-\(b\) regime can be approximated as an
impulsive acceleration of magnitude \(\sim b^{-2}\) and duration
\(\sim b\), producing a final \(y\) velocity of \(\sim b^{-1}\).  Since the
\(x\) velocity is constant, the total deflection angle is also of
order \(\sim b^{-1}\).  The overlap of the outgoing trajectories produces
a dense concentration of grains at the inner edge, which is roughly
parabolic in shape.  However, for \(b < R\starstar\) the remorseless
advance of the magnetic field does not allow the grains to slow down
and turn round, as they do in the non-magnetic and parallel-field
cases.  As a result, no dense shell forms in the apex region, but
instead there is a diffuse minimum in the density of grains around the
star due to the high grain velocities reached there.  This means that
the apparent morphology of a pure dust wave becomes very sensitive to
the radial dependence of the grain emissivity.  If this is
sufficiently steep, then the apex would coincide with the position of
the star, although in practice the presence of a wind-supported bow
shock, however small, will complicate the picture.

>>>>

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/dust-trajectories}
  (b)\\
  \includegraphics[width=\linewidth]{figs/dust-divergent}
  \caption[Dust grain trajectories]{Dust grain trajectories under
    influence of a repulsive central \(r^{-2}\) radiative force.
    (a)~A parallel stream of dust grains approach from the right at a
    uniform velocity and with a variety of impact parameters (initial
    \(y\)-coordinate). The central source is marked by a red star at
    the origin, and its radiative force deflects the trajectories into
    a hyperbolic shape, each of which reaches a minimum radius marked
    by a small black square.  The incoming hyperbolic trajectories are
    traced in gray and the outgoing trajectories are traced in red.
    The locus of closest approach of the outgoing trajectories is
    parabolic in shape (traced by the thick, light gray line) and this
    constitutes the inner edge of the bow wave.  (b)~The same but for
    a divergent stream of dust grains that originates from a source on
    the \(x\) axis at a distance \(D = 10 R\starstar\) from the
    origin.  In this case, the inner edge of the bow wave is
    hyperbolic and the parallel stream result is also shown (inner
    thick light gray line) for comparison.}
  \label{fig:dust-trajectories}
\end{figure}

@@

If \(\frad\) is the only force experienced by the grain, then it will
move on a \textit{ballistic} trajectory, determined by its initial
speed at large distance, \(v_\infty\), and its impact parameter, \(b\).
For \(b = 0\), the grain radially approaches the source with initial
radial velocity \(-v_\infty\), which is decelerated to zero at the distance
of closest approach, \(R\starstar\), given by energy conservation:
\begin{equation}
  \label{eq:dust-r0}
  R\starstar = \frac{\kappa\grain L} {2 \pi c v_\infty^2} \ ,
\end{equation}
where we have defined a frequency-averaged single-grain opacity
(\si{cm^2.g^{-1}}) as
\begin{equation}
  \label{eq:kappa-grain}
  \kappa\grain = \frac{\pi a^2}{m\grain L} \int_0^\infty \Qp \, L_\nu \, d\nu \ ,
\end{equation}
in which \(m\grain\) is the grain mass and \(L\) is the bolometric
source luminosity.  The grain then turns round and recedes from the
source along the same radius, reaching a velocity of \(+v_\infty\) at large
distance.  Note that \(R\starstar\) as given by
equation~\eqref{eq:dust-r0} is almost the same as Paper~I's
equation~(6), but with the important difference that it is for a
single grain considered in isolation, rather than a well-coupled dusty
plasma.  Since we are here ignoring collisional effects, there is no
pressure, and therefore nothing to stop the spatial coexistence of an
inbound and outbound dust stream.  For the well-coupled case, this is
not possible and a shocked shell must form (see Paper~I's Fig.~5b).

@@

If the incoming dust grains initially travel along parallel
trajectories with varying \(b\), but the same \(v_\infty\), then deflection
by the radiative force will form a bow-shaped dust wave around the
radiation source, as shown in Figure~\ref{fig:dust-trajectories}.
However, the inner edge of the dust wave, \(R_{\text{in}}(\theta)\) is not
given by the closest approach along individual trajectories,
\(R\grain(\thm; b)\), but instead must found by minimizing
\(R\grain(\theta; b)\) over all \(b\) for each value of \(\theta\), which yields
\begin{equation}
  \label{eq:dust-r-in}
  \frac{R_{\text{in}}(\theta)} {R\starstar} = \frac{2}{1 + \cos\theta} \ .
\end{equation}
This is the polar form of the equation for the confocal parabola,
which is discussed in detail in \S~\ref{Q-sec:conic} and
Appendix~\ref{Q-app:parabola} of \citet{Tarango-Yong:2018a}.  In that
paper, the dimensionless quantities \textit{planitude} \(\Pi\) and
\textit{alatude} \(\Lambda\) are introduced as a way of efficiently
characterizing bow shapes.  The confocal parabola has planitude and
alatude of \(\Pi = \Lambda = 2\) and these are unchanged under projection at
any inclination.

@@

We will show later in \S~\ref{sec:magn-effects-grain} that for
sufficiently small grains the Larmor magnetic gyration radius,
\(r\B\), is small compared with other length scales of interest, and
so the grains are effectively tied to the magnetic field lines.  In
this approximation, we can calculate the grain dynamics in the
drag-free limit using \(f\rad\) as the sole force as above, but this
time allowing acceleration only along the field lines.  Assuming a
uniform magnetic field, the only extra parameter needed is
\(\theta\B\), the angle between the field direction and the direction of
the dust stream (assumed to be plane parallel).

@@

For \(\theta\B = \ang{90}\), the guiding center is forced to move at a
constant speed in the \(x\) direction, so that \(x = -v_\infty t\), while
the motion in the \(y\) direction obeys the ODE:
\begin{equation}
  \label{eq:ode-perp-bfield}
  \frac{d^2 y}{d x^2} = \tfrac12 R\starstar  \,
  y \, \bigl( x^2 + y^2\bigr)^{-3/2} \ .
\end{equation}
We have been unable to find an analytic solution to this equation, but
a numerical solution is shown in Figure~\ref{fig:inertia-thB90}.  When
the impact parameter is larger than \(b \sim R\starstar\), the
trajectories are very similar to in the non-magnetic case
(Fig.~\ref{fig:dust-trajectories}a).  As shown in
Figure~\ref{fig:inertia-thB90}b, the interaction of the grain with the
radiation field in this large-\(b\) regime can be approximated as an
impulsive acceleration of magnitude \(\sim b^{-2}\) and duration
\(\sim b\), producing a final \(y\) velocity of \(\sim b^{-1}\).  Since the
\(x\) velocity is constant, the total deflection angle is also of
order \(\sim b^{-1}\).  The overlap of the outgoing trajectories produces
a dense concentration of grains at the inner edge, which is roughly
parabolic in shape.  However, for \(b < R\starstar\) the remorseless
advance of the magnetic field does not allow the grains to slow down
and turn round, as they do in the non-magnetic and parallel-field
cases.  As a result, no dense shell forms in the apex region, but
instead there is a diffuse minimum in the density of grains around the
star due to the high grain velocities reached there.  This means that
the apparent morphology of a pure dust wave becomes very sensitive to
the radial dependence of the grain emissivity.  If this is
sufficiently steep, then the apex would coincide with the position of
the star, although in practice the presence of a wind-supported bow
shock, however small, will complicate the picture.  Since there is no
unambiguous definition of the star--apex distance in this case, it is
not possible to define the shape parameters \(\Pi\) and \(\Lambda\) either.

### 2019-03-14 papers/Papers1234/bs-bw-dw-02.tex
Write lots of discussion for Paper II

With respect to stellar bow shocks, gas--grain decoupling has been
previously studied in the context of post-shock flow, where it is the
sudden deceleration of the gas that is the primary impetus for the
dust to separate.  The case of a cool red supergiant was simulated by
\citet{van-Marle:2011a}, where large grains present in the stellar
wind are not stopped in the inner termination shock, but are carried
through the contact discontinuity by their inertia, penetrating into
the interstellar medium.  \citet{Katushkina:2017a} simulated the
opposite case, where grains in the ambient medium become decoupled
from the gas after passing the outer bow shock, and subsequently
gyrate about the magnetic field, forming filamentary structures (see
also \citealp{Katushkina:2018a}).  In this paper, we study a different
decoupling mechanism, where it is the stellar radiation force acting
on the grains that causes the separation from the gas.  This mechanism
was first proposed by \citet{Ochsendorf:2014b} to explain the infrared
emission arc around the high-mass multiple system \(\sigma\)~Ori.

The plan of the paper is as follows.
%
In \S~\ref{sec:recap-paper-i} we give some results from Paper~I that
we will need in later sections.
%
In \S~\ref{sec:gas-free-bow} we calculate analytical models of the
shape of dust waves in the drag-free limit.
% %
% In \S\ref{sec:cloudy-models-dust} we discuss the relevant dust physics
% and the Cloudy models that we employ.
%
In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
charging and dynamics, subject to radiation and drag forces, in order
to determine the \textit{rip point}, which is where gas--grain coupling
catastrophically breaks down.  This is used to determine existence
conditions for the presence of a decoupled dust wave.
%
In \S~\ref{sec:magn-effects-grain} we consider the coupling between
the grains and the plasma's magnetic field, and how this effects the
existence and structure of dust waves.
%
In \S~\ref{sec:discussion} we discuss our results in the context of observed bows.
%
In \S~\ref{sec:summary} we summarise our findings.
%
In Appendix~\ref{sec:equat-moti-grains} we provide additional
technical information on the numerical calculation of grain
trajectories.

\section{Important results from Paper~I}
\label{sec:recap-paper-i}

%% XREF \eqref{eq:Rstar}
\begin{equation}
  \label{eq:Rstar}
  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
\end{equation}

%% XREF \eqref{eq:tau-star},
\begin{equation}
  \label{eq:tau-star}
  \tau_* = \rho \kappa R_* \ .
\end{equation}

\begin{equation}
  \label{eq:wind-efficiency}
  \eta\wind  = \frac{L}{c\, \dot{M} V\wind} \ , 
\end{equation}

%% XREF \ref{eq:x-cases}
\begin{equation}
  \label{eq:x-cases}
  R_0 \approx
  \begin{cases}
    \text{RBS (\(\tau_*^2 > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
    \text{RBW (\(\eta\wind < \tau_*^2 < 1\)):} & 2 \, \tau_* \, R_* \\
    \text{WBS (\(\tau_*^2 < \eta\)):} & \eta\wind^{1/2} \, R_*  
  \end{cases}
\end{equation}

\begin{align*}
  \label{eq:stellar-parameters}
  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
\end{align*}
where \(\bar{m}\) is the mean mass per hydrogen nucleon
(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
abundances).

%% XREF \ref{eq:wind-eta-typical}
\begin{equation}
  \label{eq:wind-eta-typical}
  \eta\wind = \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1}
\end{equation}

%% XREF \ref{eq:taustar-typical}
%% XREF \ref{eq:Rstar-typical}
\begin{align}
  \label{eq:Rstar-typical}
  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:taustar-typical}
  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \ .
\end{align}

@@

\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grants Programa de Apoyo a Proyectos de Investigación
e Inovación Tecnológica IN112816 and IN107019.  This work has made
extensive use of Python language libraries from the SciPy
\citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
  Astropy-Collaboration:2018a} projects.

>>>>

With respect to stellar bow shocks, gas--grain decoupling has been
previously studied in the context of post-shock flow, where it is the
sudden deceleration of the gas that is the primary impetus for the
dust to separate.  The case of a cool red supergiant was simulated by
\citet{van-Marle:2011a}, where large grains present in the stellar
wind are not stopped in the inner termination shock, but are carried
through the contact discontinuity by their inertia, penetrating into
the interstellar medium.  \citet{Katushkina:2017a} simulated the
opposite case, where grains in the ambient medium become decoupled
from the gas after passing the outer bow shock, and subsequently
gyrate about the magnetic field, forming filamentary structures (see
also \citealp{Katushkina:2018a}).  In this paper, we study a different
decoupling mechanism, where it is the stellar radiation force acting
on the grains that causes a separation from the gas \emph{before the
  stream reaches the bow shock}.  This mechanism was first proposed by
\citet{Ochsendorf:2014b} to explain the infrared emission arc around
the high-mass multiple system \(\sigma\)~Ori.

The plan of the paper is as follows.
%
In \S~\ref{sec:recap-paper-i} we give some results from Paper~I that
we will need in later sections.
%
In \S~\ref{sec:gas-free-bow} we calculate analytical models of the
shape of dust waves in the drag-free limit.
% %
% In \S\ref{sec:cloudy-models-dust} we discuss the relevant dust physics
% and the Cloudy models that we employ.
%
In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
charging and dynamics, subject to radiation and drag forces, in order
to determine the \textit{rip point}, which is where gas--grain coupling
catastrophically breaks down.  This is used to determine existence
conditions for the presence of a decoupled dust wave.
%
In \S~\ref{sec:magn-effects-grain} we consider the coupling between
the grains and the plasma's magnetic field, and how this effects the
existence and structure of dust waves.
%
In \S~\ref{sec:discussion} we discuss our results in the context of
previous studies.
%
In \S~\ref{sec:summary} we summarise our findings.
%
In Appendix~\ref{sec:equat-moti-grains} we provide additional
technical information on the numerical calculation of grain
trajectories.

\section{Recapitulation of Paper~I}
\label{sec:recap-paper-i}

In Paper~I, we found approximate expressions for the bow radius in each of the three regimes discussed in the introduction: 
%% XREF \ref{eq:x-cases}
\begin{equation}
  \label{eq:x-cases}
  R_0 \approx
  \begin{cases}
    \text{RBS (\(\tau_*^2 > 1\)):} & (1 + \eta\wind)^{1/2} \, R_*  \\
    \text{RBW (\(\eta\wind < \tau_*^2 < 1\)):} & 2 \, \tau_* \, R_* \\
    \text{WBS (\(\tau_*^2 < \eta\)):} & \eta\wind^{1/2} \, R_*  
  \end{cases}
\end{equation}
In these expressions, we use a fiducial radius
%% XREF \eqref{eq:Rstar}
\begin{equation}
  \label{eq:Rstar}
  R_* = \left(\frac{L}{4\pi c \rho v_\infty^2}\right)^{1/2} \ ,
\end{equation}
a fiducial optical depth
%% XREF \eqref{eq:tau-star},
\begin{equation}
  \label{eq:tau-star}
  \tau_* = \rho \kappa R_* \ ,
\end{equation}
and a factor that describes the efficiency of the stellar wind as the fraction of the stellar radiation momentum that is converted to wind momentum
\begin{equation}
  \label{eq:wind-efficiency}
  \eta\wind  = \frac{c\, \dot{M} V\wind}{L} \ .
\end{equation}
Paper~I's equation~(11) allows a more exact value for \(R_0\) to be
found numerically in intermediate cases.  Note that \(R_0\) is the
star--apex distance measured along the symmetry axis of the bow
\citetext{see \citealp{Tarango-Yong:2018a} for explanation of
  nomenclature and discussion of bow shapes}, and is calculated in the
limit that the momentum transfer occurs at a surface.  In cases where
the shell's finite width is significant, \(R_0\), should correspond
approximately to the astropause (contact discontinuity) in the WBS
regime, or a UV optical depth of unity (as measured from the star) in
the RBS regime.  The total perpendicular optical depth of the shell to
stellar radiation can be found as
\begin{equation}
  \label{eq:actual-tau}
  \tau = \frac{R_0}{R_*} \, \tau_* \ .
\end{equation}

In the foregoing, we employ the stellar bolometric luminosity, \(L\),
wind mass-loss rate, \(\dot{M}\), and terminal velocity, \(V\wind\),
together with the ambient stream's mass density, \(\rho\), relative
velocity \(v_\infty\), and effective dust opacity, \(\kappa\).  It is convenient
to define dimensionless versions of these parameters by normalizing to
typical values:
\begin{align*}
  % \label{eq:stellar-parameters}
  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
\end{align*}
where \(\bar{m}\) is the mean mass per hydrogen nucleon
(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
abundances).  In terms of these dimensionless parameters,
equations~(\ref{eq:Rstar}--\ref{eq:wind-efficiency}) take the
convenient forms:
%% XREF \ref{eq:wind-eta-typical}
%% XREF \ref{eq:taustar-typical}
%% XREF \ref{eq:Rstar-typical}
\begin{align}
  \label{eq:Rstar-typical}
  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:taustar-typical}
  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:wind-eta-typical}
  \eta\wind &= \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1} \ .
\end{align}

@@

\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grants Programa de Apoyo a Proyectos de Investigación
e Inovación Tecnológica IN112816 and IN107019.  This work has made
extensive use of Python language libraries from the SciPy
\citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
  Astropy-Collaboration:2018a} projects.  We thank Olga Katushkina for useful discussions.

### 2019-03-14 papers/Papers1234/sec-dust-wave-discussion.tex
Write lots of discussion for Paper II

In molecular clouds:  \citet{Hopkins:2016a, Lee:2017a} say they
decouple. \citet{Tricco:2017a} says they don't.  But then
\citet{Mattsson:2019a} say they do.

In \citep{Akimkin:2015a} they used the drift approximation (ignored
grain inertia effects) and also ignore back reaction on gas. In
\citet{Akimkin:2017a} they do include back reaction.

Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a}

Survival of dust grains.  Sputtering \citep{Draine:2011a}.  Radiative Torque Disruption \citep{Hoang:2018a}.

>>>>

In this section we place our results in the context of previous work
on gas--grain coupling in the environs of high-mass stars.  We
concentrate on conceptual and theoretical aspects, postponing
empirical questions about particular sources for later papers.

The distinction that we draw in \S~\ref{sec:exist-cond-separ} between
inertia-confined dust waves and drag-confined dust waves is novel.
However, the concept of the \textit{rip point} can be found in
previous works, although not under that name and it has generally been
assumed to be of little interest.  For instance, Figure~8 of
\citet{Draine:2011a} clearly shows the discontinuity in drift velocity
that occurs at small radii within an \hii{} region (differences from
our own Figs.~\ref{fig:multi-dustprops} and~\ref{fig:drift-gn} are due
to \citeauthor{Draine:2011a}'s assumption of constant grain
potential).  However, the region of supersonic drift involves a very
small fraction of the total dust in the \hii{} region, so it was not
relevant to the concerns of that paper. Similarly, in \S~3.1 of
\citet{Hopkins:2018c} the possibility is raised of a ``decoupling
instability'' in the case that coupling strength decreases with
increasing slip velocity, but they go on to dismiss this as physically
irrelevant.  On the contrary, we show in this paper that it \emph{is}
relevant so long as the grain potential is high, so that a distinct
local maximum occurs in the drag-versus-velocity profile (see
Fig.~\ref{fig:gas-grain-drag-photoionized}).  In \S~9 of
\citet{Hopkins:2018a}, various issues relating to grain charging and
drag are discussed.  The quantity
\(e_{\text{rad}} / e_{\text{therm}}\) from \S~9.1.4 of that paper is
the same as our radiation parameter, \(\Xi\).  In \S~9.2.3 they give an
expression for the critical radius that divides subsonic from
supersonic drift, which is exactly equivalent to our
equation~\eqref{eq:Rdag-over-Rstar} for the rip point radius.  The
parameters assumed by \citeauthor{Hopkins:2018a} yield
\(\Xi_\dag = 3200\), which is within the range of values that we find for
O~stars in Table~\ref{tab:Xi-rip}.

\citet{Akimkin:2017a} studied the effect of radiation pressure on the
time-dependent evolution of an \hii{} region, taking full account of
dynamical coupling between grains and gas, thus extending a previous
study \citep{Akimkin:2015a} that had ignored the back-reaction on the
gas (see our \S~\ref{sec:back-reaction-gas}).  They found that the
dust completely decouples from the gas in the zone around the star
(\(< \SI{0.2}{pc}\) on timescales \(\sim \SI{0.5}{Myr}\)), which produces
an inner dust hole but partially eliminates the inner gas density hole
that is found in models that assume perfect coupling
\citep{Mathews:1967a, Draine:2011a, Kim:2016b}. The decoupling is more
pronounced for stars of lower effective temperature, which is probably
related to the fact that we find the critical radiation parameter
\(\Xi_\dag\) to be lower for B~stars than for O~stars
(Table~\ref{tab:Xi-rip}).  A similar dust hole for the central region
is found by \citet{Ishiki:2018a}.

The gas--grain decoupling that we have discussed so far occurs at high
radiation parameter, \(\Xi \sim 1000\), but there is another regime of
potential decoupling that occurs at low \(\Xi\).  It has long been
recognized \citep{Gail:1979a} that Coulomb gas--grain coupling should
weaken in the outer zones of an \hii{} region due to the fact that the
grain potential passes through (or close to) zero as a result of
electron collisions becoming competitive with photoelectric ejection
as the radiation field weakens.  This is the regime around
\(\Xi = \text{\numrange{0.1}{1.0}}\) in Figure~\ref{fig:drift-gn},
giving drift velocities of order \SI{1}{km.s^{-1}} for larger grains
(\SI{0.2}{\um}), which may be sufficient to produce significant
spatial variations in grain abundance on Myr timescales
\citep{Ishiki:2018a}. It remains to be seen whether this is still true
once effects that have been neglected in existing models are accounted
for, such as the \hii{} region's magnetic field \citep{Krumholz:2007a,
  Arthur:2011a, Gendelev:2012a} and internal turbulence
\citep{Arthur:2016a}.  Yet another regime of potential decoupling
occurs in the neutral shell outside the \hii{} region
\citep{Gustafsson:2018a}, but since the drift velocity in both these
cases is much less than interesting values of the stream velocity,
\(v_\infty\), neither low-\(\Xi\) regime is relevant to dust waves.

The most detailed simulations to date of the combined dynamics of
dust, gas, and magnetic field in an OB bow was carried out by
\citet{Katushkina:2017a}, who followed the trajectories of dust
particles after passing through an MHD bow shock, under the influence
of the stellar radiation force and Lorentz force.  The gas is
decelerated in the shock, but the dust initially carries on with its
pre-shock motion, which produces a relative velocity with respect to
the plasma. The component of this velocity perpendicular to the
magnetic field induces gyration about the field lines
(cf~\S~\ref{sec:magn-effects-grain}), which forms filaments of
enhanced dust density that are oriented perpendicular to the bow axis
and with characteristic separation equal to the bulk plasma velocity
times the gyration period.  In \citet{Katushkina:2018a}, similar such
simulations are applied to observations of the runaway B1 supergiant
\(\kappa\)~Cas, moving at \(\approx \SI{30}{km.s^{-1}}\), in order to explain the
filaments of infrared dust emission seen at \SI{24}{\um}.  It is found
that the simulations can only fit the observations with very large
dust grains (\(\approx \SI{1}{\um}\)) and a very strong perpendicular
magnetic field \(v\alfven \approx \SI{20}{km.s^{-1}}\).  The stellar
parameters of \(\kappa\)~Cas are roughly those given in the last row of
Table~\ref{tab:stars} and the observed radius of the dust arc (assumed
to correspond to the astropause) is \SI{0.75}{pc} for a distance of
\SI{1}{kpc}.  The \citeauthor{Katushkina:2018a} simulations do not
explicitly include the Coulomb drag force on the dust grains, although
our own results (\S~\ref{sec:cloudy-models-dust}) suggest that this
must be important around \(\kappa\)~Cas.  \citet{Katushkina:2018a} argue
that small grains are swept out by stellar radiation before reaching
the bow shock, and this would indeed be true if drag forces were
negligible.  However, we find \(\Xi \approx 20\) for the
\(\kappa\)~Cas shell, implying strong gas--grain coupling and that even
small grains cannot be repelled by the radiation force.  The root
cause of our difference with these authors is that they are assuming a
grain potential \(\phi \sim 1\), as seen in the ISM in the Solar
neighborhood, as opposed to \(\phi \sim 10\), which is more appropriate to
the environs of an OB star.  We also note that even when the Lorentz
force vastly exceeds all other forces, it does not necessarily follow
that the other forces are unimportant.  For example, in the
magnetized dust wave models that we present in
\S~\ref{sec:tight-magn-coupl} and \S~\ref{sec:grain-traj-with}, the
Lorentz force is infinitely stronger than other forces.  Nevertheless,
the radiation and drag forces are crucial in determining the structure
of the dust waves, which is possible because the component of the
Lorentz force projected along the field lines is zero.

The survival of dust grains of different sizes in close proximity to
OB stars is something that must be considered.  Potential destruction
mechanisms include thermal evaporation, photosputtering, particle
sputtering, and radiative torque destruction.

Sputtering
\citep{Draine:2011a}.  Radiative Torque Disruption
\citep{Hoang:2018a}.

Instabilities: Resonant Drag Instability \citep{Squire:2018a, Hopkins:2018a} - application to stagnant drift case.
